Five-dimensional seismic data reconstruction using the optimally damped rank-reduction method

### 2020-11-04 odrr5d/paper.tex
2020年11月 4日 星期三 10时44分00秒 CST

%\inputdir{snrs_sigma}
%\plot{snr-n}{width=0.8\textwidth}{SNR diagrams of the different approaches with respect to the noise level (variance value). Note that the proposed approach outperforms the traditional methods more and more as the noise level increases.}
%
%\inputdir{snrs_ratio}
%
%\plot{snr-r}{width=0.8\textwidth}{SNR diagrams of the different approaches with respect to the sampling ratio (in percent). \new{It is obvious that the difference between the ORR method and the DRR method becomes larger as the sampling ratio increases. The ORR method always outperforms the other methods for all sampling ratios. }}
%
%

%\inputdir{snrs_rank}
%\plot{snr-rank}{width=0.8\textwidth}{SNR diagrams of the different approaches with respect to the selected rank. \new{The ORR method is obviously much less sensitive to the rank compared with other two methods. This phenomenon indicates that the ORR method can be applied as an adaptive method by setting a relatively large rank.}}
%
%
%\inputdir{hyper}
%\multiplot{3}{hyper-clean-xy,hyper-noisy-xy,hyper-obs-xy}{width=0.3\textwidth}{Common midpoint gather comparison for the synthetic example with hyperbolic events. (a) Clean data. (b) Noisy data. (c) Incomplete data. The blanks in (c) indicate where there are missing traces. }
%\multiplot{6}{hyper-rr-xy,hyper-drr-xy,hyper-odrr-xy,hyper-rr2-xy,hyper-drr2-xy,hyper-odrr2-xy}{width=0.3\textwidth}{Common midpoint gather comparison for the synthetic example with hyperbolic events. Top row shows results when $rank=12$. Bottom row shows results when $rank=24$. Left: Reconstructed data using the RR method. Middle: Reconstructed data using the DRR method. Right Reconstructed data using the ORR method. The SNR comparisons are shown in Table \ref{tbl:hyper}. }
%
%\multiplot{6}{hyper-rr-xy-simi,hyper-drr-xy-simi,hyper-odrr-xy-simi,hyper-rr2-xy-simi,hyper-drr2-xy-simi,hyper-odrr2-xy-simi}{width=0.3\textwidth}{Local similarity comparison for the synthetic example with hyperbolic events. Top row shows results when $rank=12$. Bottom row shows results when $rank=24$. Left: Reconstructed data using the RR method. Middle: Reconstructed data using the DRR method. Right Reconstructed data using the ORR method. The introduction of local similarity is given in \cite{yangkang2015ortho}. }

>>>>

\inputdir{snrs_sigma}
\plot{snr-n}{width=0.8\textwidth}{SNR diagrams of the different approaches with respect to the noise level (variance value). Note that the proposed approach outperforms the traditional methods more and more as the noise level increases.}

\inputdir{snrs_ratio}

\plot{snr-r}{width=0.8\textwidth}{SNR diagrams of the different approaches with respect to the sampling ratio (in percent). \new{It is obvious that the difference between the ORR method and the DRR method becomes larger as the sampling ratio increases. The ORR method always outperforms the other methods for all sampling ratios. }}

\inputdir{snrs_rank}
\plot{snr-rank}{width=0.8\textwidth}{SNR diagrams of the different approaches with respect to the selected rank. \new{The ORR method is obviously much less sensitive to the rank compared with other two methods. This phenomenon indicates that the ORR method can be applied as an adaptive method by setting a relatively large rank.}}

%
%\inputdir{hyper}
%\multiplot{3}{hyper-clean-xy,hyper-noisy-xy,hyper-obs-xy}{width=0.3\textwidth}{Common midpoint gather comparison for the synthetic example with hyperbolic events. (a) Clean data. (b) Noisy data. (c) Incomplete data. The blanks in (c) indicate where there are missing traces. }
%\multiplot{6}{hyper-rr-xy,hyper-drr-xy,hyper-odrr-xy,hyper-rr2-xy,hyper-drr2-xy,hyper-odrr2-xy}{width=0.3\textwidth}{Common midpoint gather comparison for the synthetic example with hyperbolic events. Top row shows results when $rank=12$. Bottom row shows results when $rank=24$. Left: Reconstructed data using the RR method. Middle: Reconstructed data using the DRR method. Right Reconstructed data using the ORR method. The SNR comparisons are shown in Table \ref{tbl:hyper}. }
%
%\multiplot{6}{hyper-rr-xy-simi,hyper-drr-xy-simi,hyper-odrr-xy-simi,hyper-rr2-xy-simi,hyper-drr2-xy-simi,hyper-odrr2-xy-simi}{width=0.3\textwidth}{Local similarity comparison for the synthetic example with hyperbolic events. Top row shows results when $rank=12$. Bottom row shows results when $rank=24$. Left: Reconstructed data using the RR method. Middle: Reconstructed data using the DRR method. Right Reconstructed data using the ORR method. The introduction of local similarity is given in \cite{yangkang2015ortho}. }
